---
title: "Final Project"
author: "Nick Dillner"
date: "2023-11-20"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r External References,include=FALSE}
library(tidyverse)
library(readxl)
library(ggplot2)
Water_Intake <- read_excel("Water_Intake.xlsx")
```


#### μ1, Mean Home
#### u2, Mean Office

$H0: μ1 = μ2$

$H1: μ1 > μ2$

$p-val < 0.05$
```{r}
tempWaterData <- Water_Intake%>%
                 select(Environment,Ounces)%>%
                 filter(!is.na(Environment))%>%
                 arrange(Environment)

t.test(Ounces~Environment, data=tempWaterData, alternative="greater")
```

#### We reject the H0, we have enough evidence to conclude that the mean number of ounces drank on days where I worked from home is significantly greater than the mean number of ounces drank when working in the office.


```{r}
tempWaterData <- Water_Intake%>%
                 select(Environment,Ounces)%>%
                 filter(!is.na(Environment))%>%
                 arrange(Environment)

tempWaterData <- tempWaterData%>%
                 group_by(Environment)%>%
                 summarise(OuncesMean=mean(Ounces))

ggplot(tempWaterData,aes(x=Environment,y=OuncesMean,fill=Environment))+geom_col(color="black",lwd=1)+geom_text(aes(label=OuncesMean),vjust=2,colour="white")+labs(title="Water Intake",x="Environment",y="Mean Ounces of Water")
```






